---
title: "Almond Sensitivity Assignment 3"
author: "Patty Park  & Vanessa Salgado"
output:
  html_document: default
  code_folding: hide
  toc: true
  toc_float: true
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
#call in libraries
library(tidyverse)

library(purrr)

library(ggpubr)

library(here)

#call in r scripts
source(here("R", "gross_revenue.R"))
source(here("R", "almond_yield.R"))
source(here("R", "CopyOfalmond_yield.R"))
source(here("R", "almond_profit_model.R"))

```


```{r}
#call in climate data csv
climate_data <- read_csv(here("Data", "clim.csv"))

```

```{r}
#use almond_yield function
total_almond_yield <- CopyOfalmond_yield(climate_data)

#use gross_revenue function
total_gross_revenue <- gross_revenue(total_almond_yield[4])

#use almond_profit_model function
almond_profit_model(gross_revenue = total_gross_revenue, almond_yield = total_almond_yield[4])
```



In your same groups -

-   Develop a profit model for your almond yield (you can make this up - think about what the parameters would be)

    -   you might assume a baseline profit and then adjust according to the anomaly\

    -   there are many ways to combine the almond yield and profit functions; you can have the profit function "call"/use the almond yield function; or create a wrapper function that calls them in sequence (first the almond yield and then the profit function)

-   **Ideas for a profit model:**

    -   **define the range: year? month?**

    -   **gross farm revenue(inputs): sales(almond_yield \* price per almond)?, year**

    -   **expenses(parameters): water usage, loss of almond product**

    -   **income(output): income = gross farm revenue - expenses** (want to normalize profits with discount rate. not required but shouldn't be complicated to apply it)

    -   from lecture 4-informal analysis:We will use output from our solarpv function as input into a function that estimates profit given a price - and also 'calls' another function to compute net present value `compute_NPV`

        -   **inputs: value, time, discount rate**
        -   **output net present value of input value provide as some time in the future**

-   Do a simple informal sensitivity analysis of almond yield profit using at least 2 parameters

```{r}
#define the samples to create a uniform distribution
nsamples = 300
deviation = 0.15
base_thresh = 9000
gallons = runif(min=base_thresh-deviation*base_thresh,
                max = base_thresh+deviation*base_thresh, n=nsamples)

#generate samples for eff parameter
eff = rnorm(mean=0.6, sd = 0.1, n=nsamples)

#bind the two together onto a dataframe
water_parms = cbind.data.frame(eff, gallons)

# use pmap 
# takes function name and then names of all parameters that don't change
gallon_pmap = water_parms %>% pmap(~almond_profit_model( 
  almond_yield = total_almond_yield[4],
  gross_revenue = total_gross_revenue,
  gallons =.x,
  acres = 10, 
  prop_of_loss = 0.25,  
  price_of_water = 0.007,  
  price_per_ton = 4000))

#View to see what the dataframe looks like and see how many we got
gallon_pmap[[1]]
length(gallon_pmap)

#extract results from the two list created
gallon_extract = map_df(gallon_pmap,`[`) #for gallon parameter
#add the parameter values for each run
gallon_extract = cbind.data.frame(gallon_extract, water_parms)
```

```{r}
#define the samples to create a uniform distribution
nsamples = 300
deviation = 0.15
base_thresh = .25
prop_of_loss = runif(min=base_thresh-deviation*base_thresh,
                max = base_thresh+deviation*base_thresh, n=nsamples)

#generate samples for eff parameter
eff = rnorm(mean=0.6, sd = 0.1, n=nsamples)

#bind the two together onto a dataframe
loss_parms = cbind.data.frame(eff, prop_of_loss)

# use pmap 
# takes function name and then names of all parameters that don't change
loss_pmap = loss_parms %>% pmap(~almond_profit_model( 
  almond_yield = total_almond_yield[4],
  gross_revenue = total_gross_revenue,
  gallons = 9000,
  acres = 10, 
  prop_of_loss = .x,  
  price_of_water = 0.007,  
  price_per_ton = 4000))

#View to see what the dataframe looks like and see how many we got
loss_pmap[[1]]
length(loss_pmap)


#extract results from the two list created
loss_extract = map_df(loss_pmap,`[`) #for loss parameter
#add the parameter values for each run
loss_extract = cbind.data.frame(loss_extract, loss_parms)

```

    -   **choose 2 parameters to change**

-   Create 2 graphs of the results - you can decide what is the most meaningful graph

```{r}
#create graphs
p1 = ggplot(gallon_extract, aes(gallons, gross_revenue, col=eff))+geom_point(cex=2)+
  labs(y="Gross revenue (price/acre)", x="Gallons of water (gal)")
p2 = ggplot(gallon_extract, aes(eff, gross_revenue, col=gallons))+geom_point(cex=2)+
  labs(y="Gross revenue (price/acre)", x="Efficiency")
ggarrange(p1,p2)
```


-   Write a short paragraph (in the Rmarkdown document) to summarize you interpretation of your model results (e.g what do 'take away' from your model and sensitivity analysis)
